---
title: "APELAFICO integral study"
output:
  html_document:
    df_print: paged
  word_document: default
  pdf_document: default
header-includes:
- \usepackage{lscape}
- \newcommand{\blandscape}{\begin{landscape}}
- \newcommand{\elandscape}{\end{landscape}}
---
  
```{r setup, include=FALSE}
library(knitr)
knitr::opts_chunk$set(comment = NA)

rm(list=ls())

library(ggplot2)
library(tidyverse)
library(lubridate)
library(icesTAF)
library(suncalc)
library(pander)

options(scipen = 999)

setwd('Y:/APELAFICO/')

sourceDir(file.path('.','function'))

figurePath    <- file.path('.','figures')
dataPath      <- file.path('.','data')
resultPath    <- file.path('.','results')
```

**Section 1: data processing**
*WBAT data*
There is WBAT data at both 70khz CW and 200khz FM (asynchronous pinging). The data are annotated with labeling bottom and surface lines.

For both frequencies, SA (~fish biomass) is exported using a threshold on sv (volume backscattering), meaning all above this treshold is considered fish. Here, the data are exported at thresholds ranging -60dB to -50dB in 1 dB steps.

For the 200khz FM, a dedicated processing is in place to: 1) track the targets with a target detection algorithm, 2) extracts tracks and corresponding frequency spectrum. This is currently work in progress.

**Table 1.1. overview of WBAT data.**
```{r echo=FALSE, fig.align="center", fig.asp=0.6, message=FALSE, warning=FALSE}
WBAT.tab <- read.csv('Z:/APELAFICO/LSSS/survey_db.csv')
WBAT.tab <- WBAT.tab[,c(1:5,8,9)]
WBAT.tab$dataSet_station <- paste0(WBAT.tab$dataSet,'_',WBAT.tab$station)

pander::pandoc.table(WBAT.tab[,1:(dim(WBAT.tab)[2]-1)],
                     style="simple", split.tables=200, justify="right", missing=".")

```
*CPOD data*
CPOD data are available alongside all WBAT recordings expect HKZ and HKN data sets. All the data have been processed with click train classification (using CPOD.exe) and further bluzz click classification, using gaussian mixture models.

**Table 1.2. overview of CPOD data.**
```{r echo=FALSE, fig.align="center", fig.asp=0.6, message=FALSE, warning=FALSE}
CPOD.tab <- read.csv('Z:/APELAFICO/CPOD_processing/data_mapping.csv')
CPOD.tab$dataSet_station <- paste0(CPOD.tab$dataSet,'_',CPOD.tab$station)

pander::pandoc.table(CPOD.tab,
                     style="simple", split.tables=200, justify="right", missing=".")

```

**Section 2: results**


**Figure 2.1. WBAT/CPOD time series.**
```{r echo=FALSE, fig.align="center", fig.asp=0.6,out.width="80%", message=FALSE, warning=FALSE} 
load(file.path(dataPath,'CPOD_all.RData'))

CPOD.all$station[CPOD.all$station == "267878"] <- "267838"

CPOD.all$dataSet_station <- paste0(CPOD.all$dataSet,'_',CPOD.all$station)

WBAT.tab <- WBAT.tab[WBAT.tab$SA_exported == 1,]

flagFirst.all <- T
for(stationSet in unique(WBAT.tab$dataSet_station)){
  tab.filt <- WBAT.tab[WBAT.tab$dataSet_station == stationSet,]
  
  # Read all data in the set of station+data set
  flagFirst <- T
  for(idxDataSet in tab.filt$surveName){
    load(file.path(dataPath,paste0('WBAT_',idxDataSet,'.RData')))
    WBAT.all <- subset(WBAT.all,depth == 0)
    
    if(flagFirst){
      WBAT.join <- WBAT.all
      flagFirst <- F
    }else{
      WBAT.join <- rbind(WBAT.join,WBAT.all)
    }
  }
  
  # summarize WBAT data per intervals
  WBAT.summary <- WBAT.join %>% group_by(treshold,IDinter,frequency,chunk) %>% summarize(dataSet_station=stationSet,
                                                                                          station=unique(station),
                                                                                         dataSet=unique(dataSet),
                                                                                          SA=mean(SA,na.rm=T),
                                                                                         datetime=first(datetime),
                                                                                         depthIntegration=first(depthIntegration))
  
  
  
  mySunlightTimes <- getSunlightTimes(date = as.Date(WBAT.summary$datetime),
                                      lat = 51.65512058,
                                      lon = 2.793530261, tz = "UTC") # hack, lat/lon needs to be inputed for each station
  WBAT.summary$hourSunset    <- hour(mySunlightTimes$sunset)+minute(mySunlightTimes$sunset)/60+second(mySunlightTimes$sunset)/60/60
  WBAT.summary$hourSunrise   <- hour(mySunlightTimes$sunrise)+minute(mySunlightTimes$sunrise)/60+second(mySunlightTimes$sunrise)/60/60
  WBAT.summary$sunset <- mySunlightTimes$sunset
  WBAT.summary$sunrise <- mySunlightTimes$sunrise
  
  WBAT.summary$dayNight <- 'night'
  WBAT.summary$dayNight[(WBAT.summary$sunrise <= WBAT.summary$datetime) & (WBAT.summary$datetime <= WBAT.summary$sunset)] <- 'day'
  
  if(!(unique(WBAT.summary$dataSet) %in% c('2022-HKZ','2023-HKN'))){
    CPOD.stationSet <- strsplit(stationSet,' ')[[1]][1]
    # summarize CPOD
    CPOD.current <- subset(CPOD.all,dataSet_station == CPOD.stationSet)
    CPOD.current$stationName  <- CPOD.current$station
    CPOD.current$lat <- NA
    CPOD.current$lon <- NA
    
    mySunlightTimes <- getSunlightTimes(date = as.Date(CPOD.current$timeIci_str),
                                        lat = 51.65512058,
                                        lon = 2.793530261, tz = "UTC") # hack, lat/lon needs to be inputed for each station
    CPOD.current$hourSunset    <- hour(mySunlightTimes$sunset)+minute(mySunlightTimes$sunset)/60+second(mySunlightTimes$sunset)/60/60
    CPOD.current$hourSunrise   <- hour(mySunlightTimes$sunrise)+minute(mySunlightTimes$sunrise)/60+second(mySunlightTimes$sunrise)/60/60
    CPOD.current$sunset <- mySunlightTimes$sunset
    CPOD.current$sunrise <- mySunlightTimes$sunrise
    
    CPOD.current$dayNight <- 'night'
    CPOD.current$dayNight[(CPOD.current$sunrise <= CPOD.current$timeIci_str) & (CPOD.current$timeIci_str <= CPOD.current$sunset)] <- 'day'
    
    res.CPOD <- format_CPOD(CPOD.current)
  }

  if(flagFirst.all){
    if(!(unique(WBAT.summary$dataSet) %in% c('2022-HKZ','2023-HKN'))){
      CPOD.all.summary <- res.CPOD$CPOD.day
    }
    WBAT.all.summary <- WBAT.summary
    flagFirst.all <- F
  }else{
    if(!(unique(WBAT.summary$dataSet) %in% c('2022-HKZ','2023-HKN'))){
      CPOD.all.summary <- rbind(CPOD.all.summary,res.CPOD$CPOD.day)
    }
    WBAT.all.summary <- rbind(WBAT.all.summary,WBAT.summary)
  }

  # make individual plot
  print(ggplot(subset(WBAT.summary,treshold %in% c(-60,-55,-50)),aes(x=datetime,y=log10(SA),col=as.factor(treshold)))+
          geom_line()+
          geom_smooth(col='black')+
          ggtitle(paste0('WBAT time series - ',stationSet))+
          facet_grid(treshold~frequency))

  if(!(unique(WBAT.summary$dataSet) %in% c('2022-HKZ','2023-HKN'))){
    print(ggplot(res.CPOD$CPOD.day,aes(x=time_day,y=buzz_ratio))+
              geom_line()+
              geom_smooth(col='black')+
              ggtitle(paste0('buzz click ratio - ',stationSet)))
  }

  print(ggplot(subset(WBAT.summary,treshold %in% c(-60,-55,-50)),aes(x=dayNight,y=log10(SA),fill=as.factor(treshold)))+
        geom_violin(draw_quantiles = c(0.25, 0.5, 0.75))+
        facet_grid(treshold~frequency)+
        ggtitle(paste0('WBAT day/night - ',stationSet)))

  if(!(unique(WBAT.summary$dataSet) %in% c('2022-HKZ','2023-HKN'))){
    print(ggplot(subset(res.CPOD$CPOD.hour,buzz_pos_minutes!=0),aes(x=dayNight,y=buzz_pos_minutes))+
          geom_boxplot()+
            ggtitle(paste0('buzz pos min - ',stationSet)))
  }
}

```

**Figure 2.2. CPOD/WBAT results per station.**
```{r echo=FALSE, fig.align="center", fig.asp=0.6,out.width="80%", message=FALSE, warning=FALSE} 
print(ggplot(WBAT.all.summary,aes(x=station,y=log10(SA)))+
  geom_violin(draw_quantiles = c(0.25, 0.5, 0.75))+
  facet_grid(frequency~dataSet,scales = 'free_x')+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
  ggtitle('SA all stations'))

print(ggplot(CPOD.all.summary,aes(x=stationName,y=pos_minutes))+
  geom_boxplot()+
  facet_wrap(~dataSet,scales = 'free')+
  ggtitle('CPOD positive minutes per station')+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)))

print(ggplot(CPOD.all.summary,aes(x=stationName,y=buzz_ratio))+
  geom_boxplot()+
  facet_wrap(~dataSet,scales = 'free_x')+
  ggtitle('CPOD buzz click ratio per station')+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)))
```

**Figure 2.3. CPOD/WBAT correlation.**
```{r echo=FALSE, fig.align="center", fig.asp=0.6,out.width="80%", message=FALSE, warning=FALSE} 

WBAT.all.summary$time_day <- as.POSIXct(cut(WBAT.all.summary$datetime, breaks = "1 day"),tz='UTC')
CPOD.all.summary$station <- CPOD.all.summary$stationName
CPOD.all.summary$dataSet_station <- paste0(CPOD.all.summary$dataSet,'_',CPOD.all.summary$station)

# combine data frames
flagFirst <- T
for(stationSet in unique(WBAT.all.summary$dataSet_station)){
  idx.WBAT <- WBAT.all.summary$dataSet_station == stationSet
  
  if(!(unique(WBAT.all.summary$dataSet[idx.WBAT]) %in% c('2022-HKZ','2023-HKN'))){
    CPOD.stationSet <- strsplit(stationSet,' ')[[1]][1]
    CPOD.current <- subset(CPOD.all.summary,dataSet_station == CPOD.stationSet)
    
    WBAT.all.day <- WBAT.all.summary[idx.WBAT,] %>% group_by(time_day,frequency,treshold) %>% summarize(SA=mean(SA,na.rm=T))
    
    df.join <- left_join(WBAT.all.day,CPOD.current,by=c('time_day'))
    df.join$station <- unique(WBAT.all.summary$station[idx.WBAT])
    df.join$dataSet <- unique(WBAT.all.summary$dataSet[idx.WBAT])
    
    if(flagFirst){
      df.join.all <- df.join
      flagFirst <- F
    }else{
      df.join.all <- rbind(df.join.all,df.join)
    }
  }
}

for(idxDataSet in unique(df.join.all$dataSet)){
  if(dim(subset(df.join.all,dataSet == idxDataSet & all_buzz!=0 & frequency == 70 & treshold == -50))[1] != 0){
    print(ggplot(subset(df.join.all,dataSet == idxDataSet & all_buzz!=0 & frequency == 70 & treshold == -50),aes(x=buzz_ratio,y=log10(SA)))+
      geom_point()+
      geom_smooth(method='lm')+
      facet_wrap(~station)+
      ggtitle(paste0('CPOD/WBAT(70) relation - ',idxDataSet)))
  }
  
  if(dim(subset(df.join.all,dataSet == idxDataSet & all_buzz!=0 & frequency == 200 & treshold == -50))[1] != 0){
    print(ggplot(subset(df.join.all,dataSet == idxDataSet & all_buzz!=0 & frequency == 200 & treshold == -50),aes(x=buzz_ratio,y=log10(SA)))+
            geom_point()+
            geom_smooth(method='lm')+
            facet_wrap(~station)+
            ggtitle(paste0('CPOD/WBAT(200) relation - ',idxDataSet)))
  }
}
```